Gammapy: A Python package for gamma-ray astronomy

### 2023-05-22 src/ms-review.tex
Clarify 1DC acronym

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \code{gammapy.data} sub-package implements the functionality to select,
read, and represent DL3 \gammaray data in memory. It provides the main user
interface to access the lowest data level. \gammapy currently only
supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
DL3 data are typically bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instrumeents, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
		observations from the 1DC dataset. The left image shows the maps of counts with the signal
		region in white and the reflected background regions for the three different observations
		overlaid in different colors. The right image shows the resulting spectral flux points and
		their corresponding log-likelihood profiles. The flux points are shown in orange, with the
		horizontal bar illustrating the width of the energy bin and the vertical bar the $1~\sigma$
		error. The log-likelihood profiles for each enetgy bin are shown in the background. The colormap
		illustrates the difference of the log-likelihood to the log-likelihood of the best fit value.
		}
	\label{fig:cta_galactic_center}
\end{figure*}
%% CN: expand 1DC acronym and add a reference, here or in the section text

>>>>

\subsection{gammapy.data}
\label{ssec:gammapy-data}
The \code{gammapy.data} sub-package implements the functionality to select,
read, and represent DL3 \gammaray data in memory. It provides the main user
interface to access the lowest data level. \gammapy currently only
supports data that is compliant with \code{v0.2} and \code{v0.3} of the \gadf data format.
DL3 data are typically bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instruments, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$20 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{
		Example of a one dimensional spectral analysis of the Galactic Center for three simulated CTA
		observations from the first CTA data challenge dataset. The left image shows the maps of counts with the signal
		region in white and the reflected background regions for the three different observations
		overlaid in different colors. The right image shows the resulting spectral flux points and
		their corresponding log-likelihood profiles. The flux points are shown in orange, with the
		horizontal bar illustrating the width of the energy bin and the vertical bar the $1~\sigma$
		error. The log-likelihood profiles for each enetgy bin are shown in the background. The colormap
		illustrates the difference of the log-likelihood to the log-likelihood of the best fit value.
		}
	\label{fig:cta_galactic_center}
\end{figure*}
%% CN: expand 1DC acronym and add a reference, here or in the section text
